---
title: "HW2"
author: "Joaquin Rodriguez"
date: "9/04/2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```


```{r}
library(tidyverse)

forbes <- read.csv(file = "Forbes2000.csv", header = T)
forbes <- as.tibble(forbes)
```


## 1. Find the median profit for the companies in the US, UK, France and Germany

```{r cars}
forbes %>%
  filter(country == c("United States","United Kingdom","France","Germany")) %>% 
  group_by(country) %>%
  summarise(median = median(profits, na.rm = T))
```

## 2. Find all German companies with negative profit

```{r}
forbes %>% 
  filter(country == "Germany" &  profits < 0)
```

## 3. Find the business category to which most of the Bermuda island companies belong

```{r}
forbes %>%
  filter(country == "Bermuda") %>% 
  count(category) %>% 
  arrange(desc(n))
```

## 4. Find the 50 companies in the Forbes dataset with the highest profit. Plot sales against assets, labelling each point with approriate country name which may need to be abbreviated (using abbreviate) to avoid makeing the plot look too messy

```{r}
forbes %>% 
  arrange(desc(profits)) %>% 
  top_n(50) %>% 
  ggplot(aes(x = sales, y = assets)) +
  geom_point() +
  geom_text(aes(label = abbreviate(country)))
```

## 5. Find the average value of sales for the companies in each country

```{r}
forbes %>% 
  group_by(country) %>% 
  summarise(avg = mean(sales, na.rm = T)) %>% 
  arrange(desc(avg))
```

## 6. Find the number of companies in each country with profits above 5 billion US dollars

```{r}
forbes %>% 
  filter(profits > 5) %>% 
  group_by(country) %>% 
  count(country) %>% 
  arrange(desc(n))
```

## 7. Fit a logistic regression model on the South African Heart Disease Dataset

```{r}
heart <- 
  read.table("http://statweb.lsu.edu/faculty/li/data/SAheart.txt",
	           sep=",", header=T, row.names=1) %>% 
  as.tibble(.)
```

## 7.a) Set the 'Present' as 1 and 'Absent' as 0 for variable 'famhist'.

```{r}
heart$famhist <- 
  heart %>% 
  .$famhist %>% 
  recode(., "Present" = 1, "Absent" = 0)
```

## 7.b) There are 462 observations in the dataset. Randomly split the dataset into 400 observations as the training set. The rest 62 observations as the test set.

```{r}
train <- 
  heart %>% 
  sample_n(400, replace = F)

test <- setdiff(heart, train)
```


## 7.c) Then fit a logistic regression using 'famhist' (now become 0 and 1 binary variable) as the response and all the other variables as the explanatory variables.

```{r}
fit1 <- 
  train %>% 
  glm(formula = famhist ~ ., family = "binomial", data = .)

fit1 %>% summary

```

## 7.d) Make the prediction on the training and test sets. Using the 0.5 as the cutoff point to get the misclassification rate on the training and test sets, respectively.

```{r}
tab1 <- table(fit1$fitted.values >= 0.5, train$famhist)
tab1
## misclassification rate on train set
misstrain <- 1- sum(diag(tab1)) / sum(tab1)
misstrain

pred1 <- predict(fit1, test, type = "response")
tab1 <- table(pred1 >= 0.5, test$famhist)
tab1
## misclassification rate on test set
misstest <- 1- sum(diag(tab1)) / sum(tab1)
misstest
```

## 7.e) Find the AUC score and plot the ROC curve based on the test set performance.  

```{r}
library(AUC)
auc(roc(pred1, factor(test$famhist)))

roc <- 
  pred1 %>%
  specificity(., factor(test$famhist)) %>% 
  .$measure %>% 
  as.tibble()
names(roc) <- c("spe1")

roc <-
  roc %>% 
  mutate(sen1 = sensitivity(pred1, factor(test$famhist))$measure)

roc %>%
  ggplot() + 
  geom_line(aes(x = 1-spe1, y = sen1)) +
  labs(x = "1 - Specificity", y = "Sensitivity", title = "ROC graph") +
  annotate("text", x = 0.6, y = 0.25, label = paste("Misclassification on test data: ", round(misstest,2))) +
  geom_abline(intercept = 0, slope = 1, color = "blue")
```

