---
title: "W3"
author: "Joaquin Rodriguez"
date: "9/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 9. This question involves the use of multiple linear regression on the Auto data set.

### (a) Produce a scatterplot matrix which includes all of the variables in the data set.

```{r}
library(ISLR)
library(tidyverse)
library(ggfortify)

# Auto <- as.tibble(Auto)

pairs(Auto)
```

### (b) Compute the matrix of correlations between the variables using the function cor(). You will need to exclude the name variable, which is qualitative.

```{r}
Auto %>% 
  select(., -name) %>% 
  cor()
```

### (c) Use the lm() function to perform a multiple linear regression with mpg as the response and all other variables except name as the predictors. Use the summary() function to print the results. Comment on the output. For instance:

```{r}
lm <- 
  Auto %>%
  select(., -name) %>%
  lm(., formula = mpg ~ .)

lm.summary <- 
  lm %>%  summary()
```

#### i. Is there a relationship between the predictors and the response?
The Adjusted R`(r lm.summary$adj.r.squared`) of the model seems to signal a strong linear relationship between the the response and the predictors.

#### ii. Which predictors appear to have a statistically significant relationship to the response?
The predictors that are significant at p < 0.01 are the following:  
* displacement  
* weight  
* year  
* origin

#### iii. What does the coefficient for the year variable suggest?
The coefficient estimate for 'year' suggest that as the age of the car increases the consumption of fuel increases. In fact, the coefficeint suggest that an increase of one year makes the mpg response to increase by 0.75.

#### Use the plot() function to produce diagnostic plots of the linear regression fit. Comment on any problems you see with the fit. Do the residual plots suggest any unusually large outliers? Does the leverage plot identify any observations with unusually high leverage?

```{r}
autoplot(lm, which = 1:6, ncol = 3, label.size = 3)
```

The residuals vs Fitted plot provide a strong indication of non-linearity in the data. In fact, we can observe a u-shape of the data, suggesting that there might be a quadratic relationship in the data.  
The residuals plot suggest the presence of large ourliers for fitted values around 30 to 40lm. Furthermore, from the plot we observe evident heteroscedasticity issues as the variability of the residuals increases as the fitted values increase.  
The leverage plot identifies some observations that have a significant leverage, defined as observations with leverage higher than `r round((7+1) / length(Auto$mpg),3)` ( (p + 1) / n  ). However, the plot suggest that observation `r which(hat(model.matrix(lm)) > 0.15)` in particular has a considerably high leverage.  

#### Use the * and : symbols to fit linear regression models with interaction effects. Do any interactions appear to be statistically significant?




```{r}

#lm <- 
  Auto %>%
  select(., -name) %>%
  lm(., formula = mpg ~ . + cylinders * displacement + ) %>% 
  summary()

```




